A Massive Molecular Gas Reservoir in the $z$\,=\,2.221 Type-2 Quasar Host Galaxy SMM\,J0939+8315 lensed by the Radio Galaxy 3C220.3

### 2015-07-19 skeleton.tex
Edit since DR's comments up to before RADIO SED

%\documentclass{emulateapj}
\documentclass[twocolumn,apj,numberedappendix]{emulateapj}
\usepackage{hyperref}
\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{tleung@astro.cornell.edu}
\newcommand{\Msun}{\mbox{$M_{\odot}$}}
\newcommand{\Rsun}{\mbox{R$_{\odot}$}}
\newcommand{\Lsun}{\mbox{L$_{\odot}$}}
\newcommand{\rarr}{$\rightarrow$}
\newcommand{\CO}{\mbox{CO($J$ = 3 $\rightarrow$ 2) }}
\newcommand{\Lp}{\mbox{$L^{\prime}_{\rm CO(1-0)}$}}
\newcommand{\LpU}{\mbox{K km s$^{-1}$ pc$^2$}}
\newcommand{\eg}{{\sl e.g.,~}}
\newcommand{\ie}{{\sl i.e.,~}}
\newcommand{\pmOne}{$^{-1}$}
\newcommand\tna{\,\tablenotemark{a}}
\newcommand\tnb{\,\tablenotemark{b}}
\newcommand\tnc{\,\tablenotemark{c}}
\newcommand\tnd{\,\tablenotemark{d}}
\newcommand\tne{\,\tablenotemark{e}}
\newcommand\tnf{\,\tablenotemark{f}}
\newcommand\tng{\,\tablenotemark{g}}

%\slugcomment{{\sc Accepted to ApJ:} August 1, 2006}
\usepackage{amsmath}
\usepackage{natbib}
\citestyle{aa}
\shorttitle{Study of a strongly lensed type-2 quasar host SMG at $z$ = 2.221}
\shortauthors{Leung \& Riechers}

\begin{document}
\title{A Massive Molecular Gas Reservoir in the Type-2 Quasar Host Galaxy SMM J0939+8315 at $z$ = 2.221  lensed by the Radio Galaxy 3C220.3}
\author{T. K. Daisy Leung and Dominik A. Riechers}
\affil{Department of Astronomy, Cornell University, Space Sciences Building, Ithaca, NY 14853, USA; tleung@astro.cornell.edu}

\begin{abstract}
We report the detection of \CO line emission in SMM J0939+8315 at $z$ = 2.221, a
strongly lensed high-redshift submillimeter galaxy (SMG) using
the Combined Array for Research in Millimeter-wave Astronomy (CARMA). The lensing system consists of a
foreground radio galaxy 3C220.3 and a companion galaxy at $z$ = 0.685. This allows us to place constraints on the intrinsic properties
of the cold gas and dust in the interstellar medium (ISM) of the background SMG which hosts a type-2 quasar. Prior to correcting for lensing 
amplification, we measure a velocity-integrated \CO line intensity of $I_{\rm CO(3-2)}$ = (10.7 $\pm$ 2.1) Jy km s\pmOne,
corresponding to a lensing-corrected CO($J$ = 1 \rarr 0) line luminosity of \Lp = (2.7 $\pm$ 
blah) $\times$ 10$^{10}$ \LpU. This
translates to a molecular gas mass of $M_{\rm gas}$ = 2.2 $\times$ 10$^{10}M_\odot$. We report marginally resolved continuum 
emission from the foreground galaxy with peak flux density of $S_\nu$ = 5.56 $\pm$ 0.54 mJy
 at 104 GHz, allowing us to put constraints on the spectral energy distribution (SED) of this galaxy. We 
fit
 both an optically thick and optically thin modified blackbody models to the SED of the SMG, the preferable optically thick model  yields dust mass of $M_{\rm
dust}$ = 50.5$^{20.4}_{-20.2}$ $\times$ 10$^8$\Msun, and total infrared (IR) luminosity of $L$ = 88.5$^{+2.6}
_{-2.6}\times$10$^{12}$\Lsun, prior to lensing correction. We conclude that the properties (\eg gas mass, gas mass 
fraction, SFR) of the molecular gas reservoir in SMM
J0939+8315 based on our \CO observation is similar to other high redshift
SMGs. \\
NEED TO  FIX: 
report SFR, gas-to-dust ratio.. Comparison, etc. 
\end{abstract}
\keywords{galaxies: formation --- galaxies: high-redshift --- submillimeter: galaxies}

\section{Introduction}\label{sec:intro}
Submillimeter-selected galaxies (SMGs) are predominantly found at redshift $z \sim$ 1$-$3, during the epoch of stellar mass and 
galaxy assembly. These galaxies are luminous in submillimeter (submm) due to the re-radiation from the dust components in the
 far-infrared (FIR) wavelengths. Followup observations of SMGs discovered in large sky surveys (\eg HerMES, H-ATLAS) (cite) with sub-(mm) facilities have led to growing consensus
  of the observable properties of SMGs (cite, blah). SMG is a population of high-redshift galaxy that are typically dusty, gas-rich, 
  and luminous ($\gtrsim$ 10$^{12}$ \Lsun) in infrared with high star formation rates ($\gtrsim $ 500 \Msun yr\pmOne) \citep[\eg][]{Lagache05a}.

  To characterize the physical properties of the gas reservoirs in the ISM where active star formation takes place, carbon monoxide (CO) rotational lines have been commonly used as tracers due to the high abundance of this molecule in the ISM as well as its low excitation energy, the ground state transition line thereby directly probes the cool gas that is essential to fuel star formation \citep{Carilli13a}. Recent observations of the CO line of SMGs at $z \sim$ 1$-$3 have  
provided evidence that SMGs have large gas reservoirs typical of \textgreater 10$^{10}$\Msun. In most cases, detailed studies are carried out on SMGs that are gravitationally lensed as lensing amplifies the intrinsic luminosities of these sources, making them the brightest unveiled in large sky surveys \citep{Negrello10a,Vieira10a}. \par
One of such lens system has a peculiar configuration consisting of a SMG, SMM J0939+8315 (hereafter SMM J0939), hosting a 
type-2 quasar at $z$ = 2.221. SMM J0939 is being strongly lensed by a double-lobed Fanaroff-Riley Class II (FR-II) \citep*{Fanaroff74} radio galaxy (3C220.3) which has a 
companion galaxy B at $z$ = 0.685, separated by 1\farcs5. SMM J0939 is currently one of the brightest known lensed
SMGs, with lensing-magnified flux density of SMM J0939 $F_{\rm 250\mu m}$ = 440 $\pm$ 15 mJy. The redshift of SMM J0939 has 
been measured through the detection of CIV 1459\AA\
 and HeII 1640\AA\
line emissions \citep[hereafter H14]{Haas14}. These line detections provide conceivable evidence of active galactic nuclei (AGN) activity in this SMG, suggesting the presence of a type-2 quasar.

In this paper, we present the detection of \CO line emission in the background SMG
SMM J0939 at $z$ = 2.221 obtained with the Combined
Array for Research in Millimeter Astronomy (CARMA), and the study of the ISM in great detail. The underlying continuum at 104 GHz allows us to put constraints on the SED of the 
foreground FR-II galaxy at mm wavelengths.

This paper is organized as follows: in \S \ref{sec:obs}, we describe the
observations of the \CO line emission with CARMA; in \S \ref{sec:res}, we report the
detection of CO emission in the background galaxy, as well as continuum emission in the foreground galaxy; in \S
\ref{sec:Lens}, we present our lens modeling analysis; in \S \ref{sec:SED}, we perform SED fitting to 3C220.3
and SMM J0939, and derive the intrinsic properties of the interstellar medium (ISM) in the SMG; in \S \ref{sec:conclusions}, we
conclude our findings by comparing to other similarly bright, strongly-lensed SMGs at similar redshifts.

We adopt a standard $\Lambda$CDM cosmological model throughout this paper, with H$_0$= 69.32 km Mpc\pmOne
s\pmOne, $\Omega_{\rm M}$ = 0.286, $\Omega_\Lambda$=0.713, based on WMAP9 results \citep{Hinshaw13a}.
The luminosity distances at $z$ = 0.685 and $z$ = 2.221 are 4214 Mpc and 19052 Mpc, respectively; 1$\arcsec$
corresponds to 8.406 kpc at $z$ = 2.221, and 7.169 kpc at $z$ = 0.685.

\section{Observations}\label{sec:obs}
\subsection{CARMA} \label{sec:carmadata}
Observations of the \CO rotational transition ($\nu_{\rm rest}$ = 345.7959899 GHz) toward the background galaxy SMM
J0939 ($z$ = 2.221) were carried out using CARMA at the redshifted frequency of $\nu_{obs}$ = 107.357 GHz (2.79 mm)  (program ID: cf0142; P.I.: Riechers). The 3 mm receivers were used to cover the redshifted CO($J$ = 3 $\rightarrow$ 2) line and the nearby 2.88 mm continuum emission, employing a correlator setup providing a bandwidth of 3.75 GHz in each sideband and spectral resolution of 5.208 MHz ($\sim$14.5 km s\pmOne). The line was placed in the
upper sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$104.2609 GHz.
Observations were carried out under good
weather conditions in the E array configuration on 2014 July 12. This resulted in 1.56 hours of 15 antenna-
equivalent on-source time after discarding unusable visibility data.
The nearby source J1039+811 (0.65Jy) was observed every 20 minutes for
pointing, amplitude, and phase calibration. Mars was observed as the primary
absolute flux calibrator, and the quasar 3C273 was observed as the secondary
flux calibrator. J0927+390 was observed for bandpass calibration, yielding $\sim
$15\% calibration accuracy.
The {\sc MIRIAD} package was used to calibrate and analyze the visibility data which are deconvolved and imaged using
the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean beam size of 13$\farcs$6 $\times$ 
5\farcs8 for the upper sideband image cube. The final rms noise is $\sigma_{\rm ch}$ = 13.7 mJy beam\pmOne\ per bin with a channel width of $\sim$29 km\pmOne, and $\sigma$ = 1.825 Jy km s\pmOne\ $\rm beam^{-1}$ over a channel width of 218.7 MHz (corresponding to $\sim$610 km s\pmOne). The continuum image is created by
averaging over all the line-free channels, this yields a synthesized clean beam size of 16\farcs7 $\times$ 7\farcs2 and an 
rms noise of 0.55 mJy beam\pmOne.

\section{Results}\label{sec:res}
\subsection{New results: Continuum Emission} 
Averaging over all the line-free channels, we detect continuum emission at 10$\sigma$ significance at an averaged frequency of $\nu_{cont}$ = 104.2106 GHz ($\sim$2.9 mm) in the observed-frame, corresponding to 175.6 GHz ($\sim$1.7 mm) at $z$ = 0.685. In this lens system, the 
foreground galaxy (3C220.3) is radio-loud, we thus expect the continuum to be dominated by synchrotron emission from the foreground galaxy. We use CASA's {\sc imfit} task to estimate the peak position of the continuum emission. The deconvolved source size is 8\farcs72 $\pm$ 0\farcs69 $\times$ 3\farcs87 $\pm$ 1\farcs60, and the integrated flux density is 7.18 $\pm$ 0.69 mJy. At the peak position of the continuum emission, the peak flux density is S$_\nu$ = 5.56 $\pm$ 0.54 
mJy beam\pmOne. An overlay image of the 104 GHz continuum emission on the 9 GHz continuum measurement (H14) is shown in Figure \ref{fig:cont}. This demonstrates that at the resolution of our observation, the continuum detection is marginally resolved. It is therefore plausible that non-thermal emission from both the lobes and the radio core dominate the integrated flux density in our measurement.

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.80\textwidth]{Figure/ContPanel}
\caption{The central cross on each image indicates the position of the radio core of 3C220.3. The contour levels of the 104 GHz continuum emission start at $\pm$3$\sigma$, incrementing at steps 
of $\pm$1$\sigma$ of 0.5 mJy beam\pmOne; the contour levels of the 9 GHz continuum 
emission start at $\pm$4$\sigma$ of $\sigma$ = 0.064 mJy beam\pmOne\ and increment at steps of $\pm$2$^n\sigma$, 
where n is a positive integer.
Left: Contour map of the 104 GHz continuum emission in 3C220.3. The beam size is 16\farcs7 $\times$ 7\farcs2, at P.A. = 
-58$\degr$, as indicated in the bottom left corner. Right: Contours of the CARMA 104 GHz continuum emission (red) from the 
foreground radio galaxy 3C220.3 overlaid on the 9 GHz emission (green and grayscale) (H14). The synthesized beam size of the VLA observations is 0$\farcs$6 $\times$ 0$\farcs$2 at P.A. 
76$\degr$. 
\label{fig:cont}}
\end{figure*}

\subsection{New results: \CO line emission}
We detect \CO line emission at 5$\sigma$ significance toward the background SMG SMM J0939 at $z$ = 2.221.
The line profile in Figure \ref{fig:mom0} is extracted at the peak position of the CO emission. Fitting a four-parameter single Gaussian to the spectrum yields a peak flux density of 19.9 $\pm
$ 2.2 mJy superimposed on a continuum level of 3.46 $\pm$ 0.40 mJy, and full width at half-maximum (FWHM) of 542 $\pm$ 32 km s\pmOne. 
The spatial extent of the SMG is $\sim$5$\arcsec$ as shown in the Submillimeter Array (SMA) 1 mm dust continuum in Figure \ref{fig:mom0}. As such, the \CO emission in the SMG is spatially unresolved. We construct a velocity-integrated (0th moment) map of the \CO 
emission using the data with continuum subtracted in the visibility plane. This results in a velocity-integrated \CO line flux of $S_{\rm CO}$ = 10.7 $\pm$ 2.12 Jy km s\pmOne\ over the FWZI velocity range of $\Delta v\sim$914 km s\pmOne, the uncertainty does not include $\sim$ 15\% calibration uncertainty. We ignore primary beam correction given that the source is close to the phase center, and the source is unresolved (\ie much smaller than the primary beam size). This \CO line measurement confirms the redshift of SMM J0939 at $z$ = 2.221 $\pm$ blah.

\begin{figure*}[tbph] 
\centering
\includegraphics[width=0.8\textwidth]{Figure/LinePanel}
\includegraphics[width=0.65\textwidth]{Figure/peak28_WiderSpectrum}
\caption{The central cross on each image corresponds to the same coordinates. The contour levels start at $\pm$2$\sigma$ and $\pm$3$\sigma$ for the CARMA line emission and the SMA continuum emission, respectively, incrementing at
steps of $\pm$1$\sigma$. Top Left: Continuum-subtracted moment-0 map of the \CO line emission toward 
the background SMG with $\sigma$ = 1.8 Jy km s\pmOne\ beam\pmOne over a velocity range of $\Delta v\sim$610 km s\pmOne\ . The angular resolution is 13$\farcs$6 $\times$ 
5\farcs8, as indicated in the bottom left corner. 
Top Right: Contours of the \CO line emission (red) overlaid on the SMA 1 mm dust continuum (green; H14) with $\sigma_{\rm 1 mm}$ = 0.84 mJy beam\pmOne. The beam size of the SMA data is 1\farcs4$ \times $1\farcs2, P.A. -34\degr, as shown 
in the bottom left corner. Bottom: 
The spectrum extracted at the peak position of the CO line emission. The spectral resolution is $\Delta v$ $\sim$29 km s\pmOne\ with an rms of $\sigma_{\rm ch}$ = 12.5 mJy beam\pmOne\ per channel.
Solid black line shows the Gaussian fit to the \CO line profile. Yellow histogram shows the 
flux density as a function of velocity offset, where 0 km s\pmOne\ corresponds to $z$ = 2.221. \label{fig:mom0}}
\end{figure*}

\section{Analysis}
\subsection{Lens Modelling} \label{sec:Lens} 
To study the intrinsic properties of the background galaxy, we determine the magnification factor by performing
lens modeling using the SMA 1 mm archival data of this system. Lens modeling is carried out in the visibility
(uv-) plane using the updated version\footnote{commit: 7aee6276} of the publicly available software {\sc uvmcmcfit}\footnote{https://github.com/sbussmann/uvmcmcfit}
\citep{Bussmann15a}. The code uses an affine-invariant Markov chain Monte Carlo (MCMC) approach to sample the posterior
probability density function (PDF) of the model parameters. In the code, the surface mass densities of both
lenses are represented by singular isothermal ellipsoid (SIE) profiles, and the source is assumed to have an
elliptical Gaussian profile. The code does not include an external shear parameter.

We fix the phase center to coordinates ($\alpha$, $\delta$) (J2000) = (9:39:23.54, 83:15:26.10), the
offset positions of the lenses and source are referenced to this phase center. The primary lens (3C220.3) is
described by 5 free parameters: the angular offset relative to
the chosen phase center in the image ($\Delta \alpha_{\rm
lens0}$ and $\Delta \delta_{\rm lens0}$), the angular Einstein radius ($\theta_{\rm E,0}$), the
axial ratio ($q_{\rm lens0}$), and the position angle ($\phi_{\rm lens0}$). The secondary lens (companion B) is
described by 3 free parameters: $\theta_{\rm E,1}$, $q_{\rm lens1}$, and $\phi_{\rm lens1}$. The angular offset
of the secondary
lens is sampled with respect to ($\Delta \alpha_{\rm lens0}$ and $\Delta \delta_{\rm lens0}$) of
the primary lens.
The source (SMM J0939) is parameterized by
6 free parameters: the position of the source relative to the
primary lens ($\Delta \alpha_{\rm s}$ and $\Delta
\delta_{\rm s}$), the total intrinsic flux density ($S$), the
effective radius ($r_{\rm s} = \sqrt{a_{\rm s} b_{\rm s}}$), the axial
ratio ($q_{\rm s}$ =  $b_{\rm s}/a_{\rm s}$), and the position angle
($\phi_{\rm s}$).
The total number of free parameters is $N_{\rm free}$ = 14. The best-fit model is obtained by maximizing the
Gaussian likelihood function $ \mathcal{L} $ according to:
\begin{equation}
    \mathcal{L} = \sum_{u, v}\left( \frac{|V_{\rm data} - V_{\rm
    model}|^2}{\sigma^2} + {\rm log}(2 \pi \sigma^2) \right)
\end{equation}
\noindent where $\sigma$ is determined from the scatter in the visibilities within a
single spectral window (natural weighting).

>>>>

%\documentclass{emulateapj}
\documentclass[twocolumn,apj,numberedappendix]{emulateapj}
\usepackage{hyperref}
\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{tleung@astro.cornell.edu}
\newcommand{\Msun}{\mbox{$M_{\odot}$}}
\newcommand{\Rsun}{\mbox{R$_{\odot}$}}
\newcommand{\Lsun}{\mbox{L$_{\odot}$}}
\newcommand{\rarr}{$\rightarrow$}
\newcommand{\CO}{\mbox{CO($J$\,=\,3\,$\rightarrow$\,2) }}
\newcommand{\Lp}{\mbox{$L^{\prime}_{\rm CO(1-0)}$}}
\newcommand{\LpU}{\mbox{K\,\,km\,\,s$^{-1}$\,\,pc$^2$}}
\newcommand{\eg}{{\sl e.g.,~}}
\newcommand{\ie}{{\sl i.e.,~}}
\newcommand{\pmOne}{\mbox{$^{-1}$}}
\newcommand\tna{\,\tablenotemark{a}}
\newcommand\tnb{\,\tablenotemark{b}}
\newcommand\tnc{\,\tablenotemark{c}}
\newcommand\tnd{\,\tablenotemark{d}}
\newcommand\tne{\,\tablenotemark{e}}
\newcommand\tnf{\,\tablenotemark{f}}
\newcommand\tng{\,\tablenotemark{g}}

%\slugcomment{{\sc Accepted to ApJ:} August 1, 2006}
\usepackage{amsmath}
\usepackage{natbib}
\citestyle{aa}
\shorttitle{Study of a strongly lensed type-2 quasar host SMG at $z$\,=\,2.221}
\shortauthors{Leung \& Riechers}

\begin{document}
\title{A Massive Molecular Gas Reservoir in the $z$\,=\,2.221 Type-2 Quasar Host Galaxy SMM\,J0939+8315 lensed by the Radio Galaxy 3C220.3}
\author{T. K. Daisy Leung and Dominik A. Riechers}
\affil{Department of Astronomy, Space Sciences Building, Cornell University, Ithaca, NY 14853, USA; tleung@astro.cornell.edu}

\begin{abstract}
We report the detection of \CO line emission in the strongly-lensed submillimeter galaxy\,(SMG) SMM\,J0939+8315 at $z$\,=\,2.2212\,$\pm$\,0.0001, using  
the Combined Array for Research in Millimeter-wave Astronomy (CARMA). 
The SMG is lensed by the radio galaxy 3C220.3 and its companion galaxy at $z$\,=\,0.685. 
This measurement allows us to place constraints on the intrinsic properties
of the cold gas and dust in the interstellar medium (ISM) of the background SMG which hosts a type-2 quasar, as well as on the spectral energy distribution (SED) of the foreground radio galaxy using the marginally resolved continuum 
emission detected at an integrated flux density of $S_\nu$\,=\,7.5\,$\pm$\,1.3 mJy
 at 104 GHz.
We measure a velocity-integrated \CO line intensity of $I_{\rm CO(3-2)}$\,=\,(10.7\,$\pm$\,1.3)\,Jy\,km\,s\pmOne,
corresponding to a lensing- and excitation-corrected CO line luminosity of \Lp\,=\,(2.9\,$\pm$\,0.8)\,$\times$\,10$^{10}$\,(10.1/$\mu_{\rm L}$)\,\LpU, where $\mu_{\rm L}$ is the lensing magnification factor inferred from our lens modeling of the 1\,mm continuum emission. 
 This
translates to a molecular gas mass of $M_{\rm gas}$\,=\,(2.3\,$\pm$\,0.6)\,$\times$\,10$^{10}$\,\Msun. We 
fit optically thick and optically thin modified blackbody models to the SED of the SMG. The preferred optically thick model yields a characteristic dust temperature of $T_{\rm dust}$\,=\,63.1$^{+1.1}_{-1.3}$\,K in the rest-frame, a dust mass of $M_{\rm dust}$\,=\,(5.2\,$\pm$\,2.1)\,$\times$\,10$^8$\,\Msun, and a total infrared (IR) luminosity of $L_{\rm IR}$\,=\,(9.1\,$\pm$\,1.2)\,$\times$10$^{12}$\,\Lsun, after correcting for lensing magnification. We conclude that the intrinsics properties (\eg gas mass, gas mass 
fraction, star formation rate) of the molecular gas reservoir in SMM
J0939+8315 based on our \CO observations is similar to other high redshift
SMGs. 
\end{abstract}
\keywords{galaxies: formation --- galaxies: high-redshift --- submillimeter: galaxies}

\section{Introduction}\label{sec:intro}
Submillimeter-selected galaxies (SMGs) are predominantly found at redshifts $z$\,$\sim$\,1$-$3, during the epoch of stellar mass and 
galaxy assembly, with a tail out to $z>$ 6 \citep{Riechers13a}. 
These galaxies are luminous at submillimeter (submm) wavelengths due to the re-radiation of dust emission peaking at 
rest-frame far-infrared (FIR) wavelengths \citep{blain02a}. 
In the past $\sim$5\,\,years, considerable amounts of effort have been invested into follow-up observations of SMGs that were 
discovered in large sky surveys \citep[\eg H-ATLAS, HerMES; ][]{Eales10a,Oliver12a}, conducted using (sub)-mm facilities. These detailed studies have led to growing consensus that SMGs are a population of high-redshift galaxies that are extremely dusty, gas-rich, 
  and luminous ($\gtrsim$ 10$^{12}$ \Lsun) at the infrared wavebands, with high star formation rates \citep[$\gtrsim $ 500 \Msun yr\pmOne; \eg][]{Lagache05a}.

  To characterize the physical properties of the gas reservoirs in the ISM where active star formation takes place, carbon monoxide (CO) rotational lines have been commonly used as tracers due to its high abundance in the ISM as well as its low excitation energy; the ground state transition line thereby directly probes the cool gas that is essential to fuel star formation \citep[See \eg][]{Carilli13a}. Recent observations of CO in SMGs at $z$\,$\sim$\,1$-$3 have demonstrated that these galaxies have large gas reservoirs typical of \textgreater 10$^{10}$\Msun \citep[\eg][]{Riechers11c,Riechers11d,Ivison11a,Bothwell13a}.

Many recent follow-up observations and thus detailed studies are carried out on SMGs that are gravitationally lensed,
 as lensing amplifies the intrinsic luminosities of these sources, making them the brightest unveiled in large sky surveys \citep{Negrello10a,Vieira10a,Oliver12a}. 
A particularly interesting, peculiar submm-bright lensing system discovered serendipitously  
consists of a type-2 quasar host SMG -- SMM\,J0939+8315 (hereafter SMM\,J0939), lensed by the double-lobed Fanaroff-Riley 
Class II \citep*[FR-II; ][]{Fanaroff74} radio galaxy 3C220.3 and its
companion galaxy B at $z$\,=\,0.685, where the two lensing galaxies are separated by 1\farcs5. 
SMM\,J0939 is currently one of the brightest known lensed
SMGs, with a lensing-magnified flux density of $S_{\rm 250\mu m}$\,=\,440\,$\pm$\,15 mJy. 
Previous detections of CIV\,1459\AA\
 and HeII\,1640\AA\ line emission toward SMM\,J0939 
 place the redshift of this galaxy at $z$\,=\,2.221, and suggest the presence of a type-2 quasar,  
indicating active galactic nucleus activity in this SMG \citep[hereafter H14]{Haas14}.

In this paper, we present the detection of \CO line emission toward the background SMG obtained with the Combined
Array for Research in Millimeter Astronomy (CARMA), which refines the redshift, and permits the study of the physical conditions in the ISM of SMM\,J0939 in great detail. Our measurement of the underlying continuum emission put constraints on the SED of the different components of the foreground FR-II galaxy at mm wavelength ($\sim$104 GHz). Based on the magnification factor from our lens model, we infer intrinsic properties of SMM\,J0939 and thereby 
conclude this paper by comparing our findings to other similarly bright, strongly-lensed SMGs at $z$\,\,$\sim$\,\,2.

We adopt a standard $\Lambda$CDM cosmological model throughout this paper, with H$_0$= 69.32 km\,\,Mpc\pmOne\,\,s\pmOne, $\Omega_{\rm M}$\,=\,0.286, $\Omega_\Lambda$=0.713, based on WMAP9 results \citep{Hinshaw13a}.
The luminosity distances at $z$\,=\,0.685 and $z$\,=\,2.221 are 4214 Mpc and 19052 Mpc, respectively; 1$\arcsec$
corresponds to 8.406 kpc at $z$\,=\,2.221, and 7.169 kpc at $z$\,=\,0.685.

\section{Observations}\label{sec:obs}
\subsection{CARMA} \label{sec:carmadata}
Observations of the \CO rotational transition ($\nu_{\rm rest}$\,=\,345.7959899 GHz) toward the background galaxy SMM
J0939 ($z$\,=\,2.221) were carried out using CARMA at a redshifted frequency of $\nu_{obs}$\,=\,107.357\,\,GHz (2.79\,\,mm)  (program ID: cf0142; P.I.: Riechers). The 3\,mm receivers were used to cover the redshifted \CO line and the nearby 2.88\,mm continuum emission, employing a correlator setup providing a bandwidth of 3.75 GHz in each sideband and a spectral resolution of 5.208 MHz ($\sim$14.5 km\,\,s\pmOne). The line was placed in the
upper sideband, with the local oscillator tuned to $\nu_{\rm LO}$\,$\sim$104.2609 GHz.
Observations were carried out under good
weather conditions in the E array configuration on 2014 July 12. This resulted in 1.56 hours of 15 antenna-equivalent on-source time after discarding unusable visibility data.
The nearby source J1039+811 (0.65\,\,Jy) was observed every 20 minutes for
pointing, amplitude, and phase calibration. Mars was observed as the primary
absolute flux calibrator, and the quasar 3C273 was observed as the secondary
flux calibrator. J0927+390 was observed for bandpass calibration, yielding $\sim
$15\% calibration accuracy.
The {\sc MIRIAD} package was used to calibrate and analyze the visibility data, which are deconvolved and imaged using
the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean beam size of 11$\farcs$3\,$\times$\,6\farcs1, at a position angle of $-$56.1$\degr$ east of north for the upper sideband image cube. 
The rms noise of the data prior to continuum subtraction is $\sigma_{\rm ch}$\,=\,8.75\,\,mJy\,\,beam\pmOne\ per bin 
with a channel width of $\sim$29 km\,\,s\pmOne
% spectra
, whereas the final rms noise of the continuum subtracted data is $\sigma_{\rm ch}$\,=\,8.71\,\,mJy\,\,beam\pmOne\ per bin with 
the same channel width, and $\sigma$\,=\,1.00\,Jy\,\,km\,\,s\pmOne\,\,$\rm beam^{-1}$ over a channel 
width of 198 MHz (corresponding to $\sim$553\,\,km\,\,s\pmOne). 
%mom0
The continuum image is created by
averaging over all line-free channels, this yields a synthesized clean beam size of 11\farcs9\,$\times$\,6\farcs5, at a position angle of $-$55.9$\degr$ east of north and an 
rms noise of 0.51\,\,mJy\,\,beam\pmOne.

\section{Results}\label{sec:res}
%\subsection{New Results: Continuum Emission} 
\subsection{New Results: 3C220.3} 
Averaging over all line-free channels, we detect continuum emission at 9$\sigma$ significance at an averaged frequency of $\nu_{cont}$\,=\,104.2106 GHz ($\sim$2.9 mm) in the observed-frame, corresponding to 175.6 GHz ($\sim$1.7 mm) at $z$\,=\,0.685. In this lens system, the 
foreground galaxy (3C220.3) is radio-loud, we thus expect the continuum emission to be dominated by the foreground galaxy (see \S \ref{sec:SEDFg} for details). We use CASA's {\sc imfit} task to estimate the peak position of the continuum emission. The deconvolved source size is (10\farcs9\,$\pm$\,4\farcs0)\,$\times$\,(3\farcs4\,$\pm$\,2\farcs1), and the integrated flux density is 7.50\,$\pm$\,1.30\,\,mJy. At the peak position of the continuum emission, the peak flux density is S$_\nu$\,=\,4.91\,$\pm$\,0.54\,\,mJy\,\,beam\pmOne. An overlay image of the 104 GHz continuum emission on the 9 GHz continuum measurement (H14) is shown in Figure \ref{fig:cont}. This demonstrates that at the resolution of our observations, the continuum emission is marginally resolved. It is therefore plausible that non-thermal emission from both the lobes and the radio core dominate the integrated flux density in our measurement.

The frequency range of our observations covers the HCO$^+$(2$-$1), HNC($J$\,=\,2\,$\rightarrow$\,1), and H$_2$O(3$_{13}$\,$-$\,2$_{20}$) 
transition line emission in the foreground galaxy, at 
the redshifted frequencies of 105.86, 107.71, and 108.79\,\,GHz, respectively. We establish 3$\sigma$ upper limits employing a typical line width of 
$\sim$\,300\,\,km\,\,s\pmOne, based on the CO($J$\,=\,1\,$\rightarrow$\,0) line measurement in the sample of local radio galaxies \citep[$z$ $<$ 0.1; ][]{Smolcic11a}, resulting in 3$\sigma$ of 7.839\,\,Jy\,\,km\,\,s\pmOne.\\ \\
Question for DR: 3sigma using FWHM or total line width (FWZI?)

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.80\textwidth]{Figure/ContPanel.pdf}
\caption{Left: Contour map of the 104 GHz continuum emission in 3C220.3. The beam size is 11\farcs9\,$\times$\,6\farcs5, at P.A.\,=\,
$-$56$\degr$, as indicated in the bottom left corner. Right: Contours of the CARMA 104 GHz continuum emission (red) from the 
foreground radio galaxy 3C220.3 overlaid on the 9 GHz emission (green contours and grayscale; H14). The synthesized beam size of the VLA observations is 0$\farcs$6\,$\times$\,0$\farcs$2, at P.A. 
76$\degr$. The central cross on each image indicates the position of the radio core of 3C220.3. The contour levels of the 104 GHz continuum emission start at $\pm$3$\sigma$, incrementing at steps 
of $\pm$1$\sigma$ of 0.5 mJy beam\pmOne; the contour levels of the 9 GHz continuum 
emission start at $\pm$4$\sigma$ where $\sigma$\,=\,0.064 mJy beam\pmOne\ and increment at steps of $\pm$2$^n\sigma$, 
where $n$ is a positive integer.
\label{fig:cont}}
\end{figure*}
%\subsection{New Results: \CO Line Emission}
\subsection{New Results: SMM\,J0939\\ \CO Line Emission}
We detect \CO line emission at $\sim$10(?yes?no?)$\sigma$ significance toward the background SMG SMM\,J0939 at $z$\,=\,2.221.
The spatial extent of this SMG is $\sim$5$\arcsec$, as shown in the Submillimeter Array (SMA) 1\,mm dust continuum in Figure \ref{fig:mom0}; as such, the detected \CO line emission is spatially unresolved. 
The line profile in Figure \ref{fig:mom0} is therefore extracted at the peak position of the unresolved CO emission. Fitting a four-parameter single Gaussian to the spectrum yields a peak flux density of 21.83\,$\pm$\,2.68\,\,mJy, superimposed on a continuum level of 4.19\,$\pm$\,0.49\,\,mJy, and full width at half-maximum (FWHM) of 557\,$\pm$\,36\,\,km\,\,s\pmOne. 
We construct a velocity-integrated (0th moment) map of the \CO 
emission from the data after subtracting continuum emission in the visibility plane. This results in a velocity-integrated \CO line flux of $S_{\rm CO}$\,=\,10.7\,$\pm$\,1.3 Jy km\,\,s\pmOne\ over the FWZI velocity range of $\Delta v\sim$\,914 km\,\,s\pmOne, the uncertainty does not include $\sim$\,15\% calibration uncertainty. We ignore primary beam correction given that the source is close to the phase center and is unresolved (\ie much smaller than the primary beam size). Our \CO line measurement confirms the redshift of SMM\,J0939, yielding $z$\,=\,2.22122\,$\pm$\,0.00007.

\begin{figure*}[tbph] 
\centering
\includegraphics[width=0.8\textwidth]{Figure/LinePanel.pdf}
\includegraphics[width=0.65\textwidth]{Figure/smmj0939-co32_spec.eps}
\caption{Top Left: Continuum-subtracted moment-0 map of \CO line emission toward 
the background SMG with $\sigma$\,=\,1.00\,Jy\,\,km\,\,s\pmOne\ beam\pmOne\ over a velocity range of $\Delta v\sim$553\,km\,\,s\pmOne. The angular resolution is 11$\farcs$3\,$\times$\,6\farcs1, at P.A.\,=\,$-$56\degr, as indicated in the bottom left corner. 
Top Right: Contours of the \CO line emission (red) overlaid on the SMA 1\,mm dust continuum (green contours and grayscale; H14) with $\sigma_{\rm 1\,mm}$\,=\,0.84 mJy beam\pmOne. The beam size of the SMA data is 1\farcs4$ \times $1\farcs2, P.A. $-$34\degr, as shown 
in the bottom left corner. 
The central cross on each image corresponds to the same coordinates as in Figure \ref{fig:cont}. The contour levels start at $\pm$3$\sigma$, incrementing at
steps of $\pm$1$\sigma$. 
Bottom: 
Spectrum extracted at the peak position of CO line emission, with a spectral resolution of $\Delta v$ $\sim$29 km\,\,s\pmOne\, and an rms of $\sigma_{\rm ch}$\,=\,8.75 mJy beam\pmOne\ per channel.
Solid black line shows the Gaussian fit to the \CO line profile. Yellow histogram shows the 
flux density as a function of velocity offset, where the velocity scale is relative to $z$\,=\,2.221. 
%where 0 km\,\,s\pmOne\ corresponds to $z$\,=\,2.221. 
\label{fig:mom0}}
\end{figure*}
